Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-06-29 paper/arm.tex
first draft of PwT-C11
accepted anton's edit

\section{Lowering PwT-MCA to Arm}
\label{sec:arm}
For simplicity, we restrict to top level parallel composition and ignore
fences\footnote{Fences are not actions in \armeight{}, which complicates the
  theorem statements.}.

@@

\subsection{PwT-MCA Lowering 1}
\label{sec:arm1}

The optimal lowering for \armeight{} is unsound
for \PwTmca.  The optimal lowering maps relaxed access to \LDR/\STR{} and
non-relaxed access to \LDAR/\STLR{} \citep{DBLP:journals/pacmpl/PodkopaevLV19}.
In this section, we consider a suboptimal strategy, which lowers non-relaxed
reads to $(\DMBSY\SEMI\LDAR)$.  Significantly, we retain the optimal lowering
for relaxed access.  In the next section we recover the optimal lowering by
adopting an alternative semantics for \ref{pom-rf-le} and \ref{seq-le-delays}.

@@

\subsection{PwT-MCA Lowering 2}
\label{sec:arm2}

>>>>

\section{Lowering \PwTmcaTITLE{} to Arm}
\label{sec:arm}
For simplicity, we restrict to top level parallel composition.
% and ignore
% fences\footnote{Fences are not actions in \armeight{}, which complicates the
%   theorem statements.%
%   \app{Is it true? AFAIU, it isn't, they are explicitly used in definition of $\textsc{bob}$.
%     I've just found that Jade prefers to omit them in pictures.}}.
% JWR: I didn't know that!  It's better with them...

@@

\subsection{Lowering \PwTmcaTITLE{1} to Arm}
\label{sec:arm1}

The optimal lowering for \armeight{} is unsound
for \PwTmca{1}.  The optimal lowering maps relaxed access to \LDR/\STR{} and
non-relaxed access to \LDAR/\STLR{} \citep{DBLP:journals/pacmpl/PodkopaevLV19}.
In this section, we consider a suboptimal strategy, which lowers non-relaxed
reads to $(\DMBSY\SEMI\LDAR)$.  Significantly, we retain the optimal lowering
for relaxed access.  In the next section we recover the optimal lowering by
adopting an alternative semantics for \ref{pom-rf-le} and \ref{seq-le-delays}.

@@

\subsection{Lowering \PwTmcaTITLE{2} to Arm}
\label{sec:arm2}
